\subsection[Criterium Crash]{Emergency! A Criterium Crash}

Two-thirds of the way through the race, the rider in fourth place is pushing through exhaustion and struggling to keep up with the pack.
Heading in to turn 3, they hit some loose gravel on course, and are not able to make the turn.

The rider's front wheel strikes the curb, somersaulting them into a tree planted in the grass median between the curb and sidewalk.

At least three riders were closely following the first rider who crashed and all crash into the rider's bike, which is lying on the ground.

The \pbproleref{role:course_marshal} assigned to the corner notices the crash, and calls it on the radio:
``Crash at corner three.  We need medical\sidenote{%
  It is a standard practice for both USA Cycling and the ECCC that we do not transmit any identifying information over the radio about any medical incidents.
}.''

The \pbproleref{role:medical} EMTs start heading over to the crash.
Additionally, the \pbproleref{role:chief_ref} should ensure a USA Cycling official also attends the scene, to assist with scene management and to complete paperwork
for insurance\sidenote{%
  If the primary or secondary promoters are trained USA Cycling officials and are available,
  they should offer to attend the scene on behalf of the officiating team.
}.
Finally, either the \pbproleref{role:primary_promoter} or \pbproleref{role:secondary_promoter} should attend the scene, to provide any assistance they can.

While waiting for medical providers to get to the scene,
the \pbproleref{role:course_marshal} notices that several riders get up from the crash and continue racing.
The marshal notes one of the rider's numbers as the rider returns to the race,
but knows they missed several potentially injured riders who returned to the race%
\sidenote{%
  The majority of the time, course marshals, bystanders, and trained officials will not see all participants who crashed.
}.
After the initial chaos, the marshal is left with the initially injured rider and two riders affected by the crash who remain on scene.

The \pbproleref{role:course_marshal}
